---
title: "CogSci Eye-tracking Workshop 2019 - Day 5"
author: "Fabio Trecca"
date: "12/2/2019"
output:
  html_document:
#    theme: paper
    highlight: zenburn
---

### Setup ###

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.align = 'center') 
```

```{r libraries}
## Set working directory to the relevant one on your computer    
getwd()  
setwd("~/Library/Mobile Documents/com~apple~CloudDocs/4. Aarhus Universitet/4. Semester/1. Computational Modelling/1. Eyetracking workshop/rfolder/callingET")

library(pacman)
p_load("desc", "tidyverse", "lme4", "stringr", "stringi", "BBmisc", "MuMIn")
library(BBmisc) 
``` 


### Load data ###
```{r load data} 
Fixations <- read_csv('fixations2018_2019.csv') 
Saccades <- read_csv('saccades2018_2019.csv')

# Make sure variables are of the right type
Fixations <- Fixations %>%
  mutate(
    ParticipantID = as.factor(ParticipantID),
    Year = as.factor(Year),
    Task = as.factor(Task),
    ParticipantGender = as.factor(ParticipantGender),
    Item = as.factor(Item),
    #StartTime_scaled = scale(StartTime)
    #StartTime_norm = normalize(StartTime, method = "standardize", margin = 1L, on.constant = "quiet")
  )

Saccades <- Saccades %>%
  mutate(
    ParticipantID = as.factor(ParticipantID),
    Direction = as.factor(Direction),
    Year = as.factor(Year),
    Task = as.factor(Task),
    ParticipantGender = as.factor(ParticipantGender),
    Item = as.factor(Item),
    StartTime = scale(StartTime)
  )
```

```{r Filtering data} 
#Filtering out blinks  
Saccades <-  filter(Saccades, Blink == "FALSE")

# Splitting acc. to task
VS_Fixations <- filter(Fixations, Fixations$Task != "SocialEngagement" & Fixations$StartTime <= 20000 & Fixations$ParticipantID != "2018-1_1_f1")

VS_Saccades <- filter(Saccades, Saccades$Task != "SocialEngagement" & Saccades$Blink == "FALSE" & Saccades$StartTime <= 20000 & Saccades$ParticipantID != "2018-1_1_f1")

SE_Fixations <- filter(Fixations, Task == "SocialEngagement")
SE_Saccades <-  filter(Saccades, Task  == "SocialEngagement")

# Duration filtering out
VS_Fixations <- filter(VS_Fixations, StartTime <= 20000)
#SE_Fixations <- filter(SE_Fixations, StartTime <= 20000)

# Filtering out last fixations --> where they find the star
VS_Fixations <- VS_Fixations %>%
  group_by(Trial, ParticipantID) %>%
  filter(Fixation != max(Fixation))

```

```{r scale}
VS_Fixations$StartTime_scaled <- scale(VS_Fixations$StartTime)
VS_Saccades$StartTime_scaled <- scale(VS_Saccades$StartTime)
```


###### Visual search ######

#Fixation: duration
```{r Fixation duration models} 
#model 1 ---->>>> THIS IS OUR MODEL 
fix_model_vs_1 <- glmer(Duration ~ Task * StartTime_scaled + (1 + Task | Item) +  (1 + Task | ParticipantID), family = gaussian(link = log),  REML = F, VS_Fixations)

#model 2
fix_model_vs_2 <- glmer(Duration ~ Task + StartTime_scaled + (1 + Task | Item) + (1 + Task + StartTime_scaled | ParticipantID), Family = gaussian(link=log), REML = F, VS_Fixations)

#model 3
fix_model_vs_3 <- glmer(Duration ~ Task * StartTime_scaled + (1 + Task | Item) + (1 | ParticipantID) + (0 + Task | ParticipantID), REML = F, family = gaussian (link=log), VS_Fixations)

#model 4 --> NOT LEGAL obs
fix_model_vs_4 <- glmer(Duration ~ Item * StartTime_scaled + (1 + Task | Item) + (1 | ParticipantID) + (1 + Task | ParticipantID), REML = F, family = gaussian (link=log), VS_Fixations)

#model 5
fix_model_vs_5 <- glmer(Duration ~ Task * StartTime_scaled + (1 + Task | Item) + (1 | ParticipantID) + (1 + Task | ParticipantID), REML = F, family = gaussian (link=log), VS_Fixations)

#model 6
fix_model_vs_6 <- glmer(Duration ~ Task + StartTime_scaled + (1 + Task  | Item) + (1 | ParticipantID) + (1 + Task | ParticipantID), REML = F, family = gaussian (link=log), VS_Fixations)

#model 7
fix_model_vs_7 <- glmer(Duration ~ Item * StartTime_scaled + Task + (1 + Task | Item) + (1 | ParticipantID) + (1 + Task | ParticipantID), REML = F, family = gaussian (link=log), VS_Fixations)

#model 8 
fix_model_vs_8 <- glmer(Duration ~ Item + StartTime_scaled + Task + (1 + Task | ParticipantID), REML = F, family = gaussian (link=log), VS_Fixations)

#model 9
fix_model_vs_9 <- glmer(Duration ~ Item + Task + (1 + Task | ParticipantID), REML = F, family = gaussian (link=log), VS_Fixations)

#model 10
fix_model_vs_10 <- glmer(Duration ~ Item + StartTime_scaled + (1 | ParticipantID), REML = F, family = gaussian (link=log), VS_Fixations)

#model 11
fix_model_vs_11 <- glmer(Duration ~ Item + Task + (1 | ParticipantID), REML = F, family = gaussian (link=log), VS_Fixations)

#model 12
fix_model_vs_12 <- glmer(Duration ~ Item + StartTime_scaled + (1|ParticipantID), family = gaussian(link = log), VS_Fixations, REML = F)

#model 13
fix_model_vs_13 <- glmer(Duration ~ Task + StartTime_scaled + (1|ParticipantID), family = gaussian(link = log), VS_Fixations, REML = F)

# Summaries 
summary(fix_model_vs_1)                    #YES
summary(fix_model_vs_2)   #not converging
summary(fix_model_vs_3)                    #YES
summary(fix_model_vs_4)   #not converging
summary(fix_model_vs_5)                    #YES
summary(fix_model_vs_6)                    #YES
summary(fix_model_vs_7)   #not converging
summary(fix_model_vs_8)   #not converging
summary(fix_model_vs_9)   #not converging
summary(fix_model_vs_10)                   #YES
summary(fix_model_vs_11)  #not converging
summary(fix_model_vs_12)                   #YES  --> Final model - Item
summary(fix_model_vs_13)                   #YES  --> Final model - Task

# Anova to find best models
anova(fix_model_vs_1, fix_model_vs_10)

```
 
```{r R^2} 
r.squaredGLMM(fix_model_vs_12)
#              R2m        R2c
# [1,] 2.737782e-07 0.01225219

r.squaredGLMM(fix_model_vs_13)
#               R2m       R2c
#[1,] 3.010978e-07 0.0137265

### ^Both are shit. R^2m is % of variance explained by the model, R^2c is explained by model + random effects

```

```{r Cross validation} 
p_load(cvms, groupdata2, metrics, caret)
p_load(DT)

data <- fold(VS_Fixations, k = 5,
             id_col = 'ParticipantID') %>% 
  arrange(.folds)

# To specify models
fixation_models <- (c("Duration ~ Task + StartTimeS + (1 | ParticipantID)", "Duration ~ Item + StartTimeS + (1 | ParticipantID)"))
  
# To crossvalidate
CV_fix <- cross_validate(data, 
                         fixation_models, 
                         folds_col = '.folds',
                         family = 'gaussian',
                         REML = FALSE)
CV_fix


```

```{r exp transf}
summary(fix_model_vs_12)
summary(fix_model_vs_13)
fix_model_vs_12@beta[1]
exp(-0.137008)
```

Cross-validation predicts how well a model built from all the data will perform on new data. As with the test/train split, for a good modeling procedure, cross-validation performance and training performance should be close.
```{r CV fixation}
MuMIn::r.squaredGLMM(fix_model_vs_12)
MuMIn::r.squaredGLMM(fix_model_vs_13)
#             R2m        R2c
#[1,] 3.01098e-07 0.01372651
#              R2m        R2c
##[1,] 2.738067e-07 0.01225156

p_load(cvms, groupdata2)
data <- fold(VS_Fixations, k = 5,
             id_col = 'ParticipantID') %>% 
  arrange(.folds)
# To specify models
fixation_models <- (c("Duration ~ Task + StartTime_scaled + (1 | ParticipantID)", "Duration ~ Item + StartTimeS + (1 | ParticipantID)"))
  
# To crossvalidate
CV_fix <- cross_validate(data, 
                         fixation_models, 
                         folds_col = '.folds',
                         family = 'gaussian',
                         REML = FALSE)
CV_fix
p_load(Metrics)

#Get the rmse of the full model's predictions
rmse(VS_Fixations$Duration, predict(fix_model_vs_12))
rmse(VS_Fixations$Duration, predict(fix_model_vs_13))
#Evaluate RMSE
sd(VS_Fixations$Duration)
#The model performs worse than actually taking the average. 
#Very close when cross-validated though, but RMSE should be smaller than SD in a good model. 

```





#Saccades: Amplitude + velocity

AMP = how far
VEL = how fast
```{r Saccade modelling} 
#### AMPLITUDE ###
amp_model_vs_1 <- glmer(Amplitude ~ Task * StartTime + (1 + Task | Item) +  (1 + Task | ParticipantID), family = gaussian(link = log), REML = F, VS_Saccades)

amp_model_vs_2 <- glmer(Amplitude ~ Task + StartTime + (1 + Task | Item) +  (1 + Task | ParticipantID), family = gaussian(link = log), REML = F, VS_Saccades)

amp_model_vs_3 <- glmer(Amplitude ~ StartTime * Item +  (1 + Task | ParticipantID), family = gaussian(link = log), REML = F, VS_Saccades)

#summaries
summary(amp_model_vs_1)
summary(amp_model_vs_2)
summary(amp_model_vs_3)


#### VELOCITY ###
 
vel_model_vs <- glmer(MeanVelocity ~ Task * StartTime + (1 + Task | Item) +  (1 + Task | ParticipantID), family = gaussian(link = log), REML = F, VS_Saccades)

#summaries
summary(vel_model_vs)
```

```{r CV saccades}
data <- fold(VS_Saccades, k = 5,
             id_col = 'ParticipantID') %>% 
  arrange(.folds)
# To specify models
modelo <- (c("Amplitude ~ Task*StartTimeS + (1 + Task | Item) + (1 + Task | ParticipantID)", "Amplitude ~ Task + StartTimeS + (1 + Task | Item) + (1 + Task | ParticipantID)"))
  
# To crossvalidate
CV_sac <- cross_validate(data, 
                         modelo, 
                         folds_col = '.folds',
                         family = 'gaussian',
                         REML = FALSE)
CV_sac
```

# Plots
```{r wow all gathered}
VS_Fixations %>% 
  ggplot() +
  aes(x = StartTime, color = Task, y = Duration ) +
  geom_smooth(method = "lm") 

VS_Fixations %>% 
  ggplot() +
  aes(x = StartTime, color = Item, y = Duration ) +
  geom_smooth(method = "lm", se = F) + facet_wrap(~Task)

VS_Fixations %>% filter(Year == "2018")%>%
  ggplot() +
  aes(x = StartTime, color = Item, y = Duration ) +
  geom_smooth(method = "lm", se = F) + facet_wrap(~Task)

VS_Fixations %>% filter(Year == "2019")%>%
  ggplot() +
  aes(x = StartTime, color = Item, y = Duration ) +
  geom_smooth(method = "lm", se = F) + facet_wrap(~Task)

ggplot(VS_Fixations, aes(x=Task, y=Duration, color=Task)) + 
  geom_violin() +
  ylim(0, 5000) +
  labs(title ='Distribution of Duration of Fixations Acording to Task')

ggplot(allfix18, aes(x=StartTimeS, y=PupilSize, color=ParticipantGender)) + 
  geom_smooth(method = "auto", se = F) + facet_grid(Position~Gender) +
  labs(title ='Distribution of Duration of Fixations Acording to Task')

ggplot(allfix18, aes(x=Fixation, y=PupilSize, color=ParticipantGender)) + 
  geom_smooth(method = "auto", se = F) + facet_grid(Position~Gender) +
  labs(title ='Distribution of Duration of Fixations Acording to Task')

ggplot(allfix18, aes(x=Fixation, y=PupilSize, color=ParticipantGender)) + 
  geom_smooth(method = "lm", se = F) + facet_grid(Position~Gender) +
  labs(title ='Distribution of Duration of Fixations Acording to Task')

VS_Saccades %>% 
  ggplot() +
  aes(x = StartTime, color = Task, y = Amplitude ) +
  geom_smooth(method = "lm") 

VS_Saccades %>% 
  ggplot() +
  aes(x = StartTime, color = Item, y = Amplitude ) +
  geom_smooth(method = "auto", se = F) + facet_wrap(~Task)

ggplot(VS_Saccades, aes(x=Task, y=Duration, color=Task)) + 
  geom_violin() +
  ylim(0, 5000) +
  labs(title ='Distribution of Duration of Fixations Acording to Task')
```

```{r Heatmap count}
## these colors work well for heatmaps (see https://gist.github.com/kalebr/6832380)
jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF",
                                 "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

z = subset(VS_Fixations, ParticipantID ==	'2019-2_2_f22' & Item == 'fjord.jpg')

#Just heatmap
ggplot(z, aes(x = PositionX, y = 1081-PositionY)) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))),
                 contour=F, n=1000) + 
  scale_alpha(range = c(0.1, 0.6)) +
  scale_fill_gradientn(colours = jet.colors(10), trans="sqrt") + 
  # facet_wrap(~Trial) +
  ## the following lines are for aesthetic purposes only
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Heatmap for visual search task') +
  theme_bw() + theme(legend.position = 'none')

### HEATMAP W/IMAGE
img <- jpeg::readJPEG('Pics/VisualSearch/fjord.jpg')
img <- grid::rasterGrob(img, interpolate=TRUE)

#FINAL PLOT
ggplot(z, aes(x = PositionX, y = 1081-PositionY)) +
  annotation_custom(img, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), # alpha part: the vibrance of the colours are more intense when squarerooted!
                 contour=FALSE, n=1000) + 
  scale_alpha(range = c(0.1, 0.6)) +
  scale_fill_gradientn(colours = jet.colors(10), trans="sqrt") +
  # facet_wrap(~Trial) +
  ## the following lines are for aesthetic purposes only
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Heatmap for visual search task (count)') +
  theme_bw() + theme(legend.position = 'none')

```

```{r Scanpath count}
p_load(ggrepel, jpeg)

VS_Fixations %>% filter(ParticipantID == "2019-2_2_f22"& Item == 'fjord.jpg')
#COUNT task

# Ploting scan path
x = subset(VS_Fixations, ParticipantID ==	'2019-2_2_f22' & Item == 'fjord.jpg')

img <- jpeg::readJPEG('Pics/VisualSearch/fjord.jpg')
img <- grid::rasterGrob(img, interpolate=TRUE)

#Scanpath w/image
ggplot(x, aes(x = PositionX, y = 1081-PositionY)) +
  annotation_custom(img, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, fill = 'white', alpha = .02) +
  geom_path(alpha = .6, color = 'red') +
  geom_point(size = x$Duration*20,  color = '#6291D6', stroke = 1, shape = 21) +
  ggrepel::geom_text_repel(aes(label = Fixation), size = 3, color = 'blue') +
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Scanpath for visual search task') +
  theme_bw() + theme(legend.position = 'none')

#Scanpath w/o image
ggplot(x, aes(x = PositionX, y = 1081-PositionY)) +
  geom_path(alpha = .6, color = '#F0B952') +
  geom_point(size = x$Duration*20, alpha = .6, color = '#6291D6', stroke = 1, shape = 21) +
  ggrepel::geom_text_repel(aes(label = Fixation), size = 3, color = 'black') +
  # facet_wrap(~Trial) +
  ## the following lines are for aesthetic purposes only
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Scanpath for visual search task') +
  theme_bw() + theme(legend.position = 'none')
```

```{r Heatmap star}
VS_Fixations %>% filter(ParticipantID == "2019-2_2_f22"& Item == 'fjord.jpg')
#COUNT

VS_Fixations %>% filter(Item == 'fjord.jpg' & Task == 'VisualSearch_Star')
#2019-1_1_m11


## these colors work well for heatmaps (see https://gist.github.com/kalebr/6832380)
jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF",
                                 "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

z = subset(VS_Fixations, ParticipantID ==	'2019-1_1_m11' & Item == 'fjord.jpg')

#Just heatmap
ggplot(z, aes(x = PositionX, y = 1081-PositionY)) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))),
                 contour=F, n=1000) + 
  scale_alpha(range = c(0.1, 0.6)) +
  scale_fill_gradientn(colours = jet.colors(10), trans="sqrt") + 
  # facet_wrap(~Trial) +
  ## the following lines are for aesthetic purposes only
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Heatmap for visual search task') +
  theme_bw() + theme(legend.position = 'none')

### HEATMAP W/IMAGE
img <- jpeg::readJPEG('Pics/VisualSearch/fjord.jpg')
img <- grid::rasterGrob(img, interpolate=TRUE)

#FINAL PLOT
ggplot(z, aes(x = PositionX, y = 1081-PositionY)) +
  annotation_custom(img, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), # alpha part: the vibrance of the colours are more intense when squarerooted!
                 contour=FALSE, n=1000) + 
  scale_alpha(range = c(0.1, 0.6)) +
  scale_fill_gradientn(colours = jet.colors(10), trans="sqrt") +
  # facet_wrap(~Trial) +
  ## the following lines are for aesthetic purposes only
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Heatmap for visual search task (star)') +
  theme_bw() + theme(legend.position = 'none')
```

```{r Scanpath star}
p_load(ggrepel, jpeg)

VS_Fixations %>% filter(ParticipantID == "2019-1_1_m11"& Item == 'fjord.jpg')
#COUNT task

# Ploting scan path
x = subset(VS_Fixations, ParticipantID ==	'2019-1_1_m11' & Item == 'fjord.jpg')

img <- jpeg::readJPEG('Pics/VisualSearch/fjord.jpg')
img <- grid::rasterGrob(img, interpolate=TRUE)

#Scanpath w/image
ggplot(x, aes(x = PositionX, y = 1081-PositionY)) +
  annotation_custom(img, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, fill = 'white', alpha = .02) +
  geom_path(alpha = .6, color = 'red') +
  geom_point(size = x$Duration*20,  color = '#6291D6', stroke = 1, shape = 21) +
  ggrepel::geom_text_repel(aes(label = Fixation), size = 3, color = 'blue') +
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Scanpath for visual search task') +
  theme_bw() + theme(legend.position = 'none')

#Scanpath w/o image
ggplot(x, aes(x = PositionX, y = 1081-PositionY)) +
  geom_path(alpha = .6, color = '#F0B952') +
  geom_point(size = x$Duration*20, alpha = .6, color = '#6291D6', stroke = 1, shape = 21) +
  ggrepel::geom_text_repel(aes(label = Fixation), size = 3, color = 'black') +
  # facet_wrap(~Trial) +
  ## the following lines are for aesthetic purposes only
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Scanpath for visual search task') +
  theme_bw() + theme(legend.position = 'none')
```


OBS HER --> RET TIL MIT
```{r Heat map}
p_load(ggrepel, jpeg)
FixationsVS %>% filter(ParticipantID == "2019-2_2_f22"& Item == 'fjord.jpg')
#COUNT
FixationsVS %>% filter(Item == 'fjord.jpg' & Task == 'VisualSearch_Star')
#2019-1_1_m11
img <- jpeg::readJPEG('Pics/VisualSearch/fjord.jpg')
img <- grid::rasterGrob(img, interpolate=TRUE)
x = subset(FixationsVS, ParticipantID ==	'2019-2_2_f22' & Item == 'fjord.jpg')
ggplot(x, aes(x = PositionX, y = 1081-PositionY)) +
  annotation_custom(img, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, fill = 'white', alpha = .02) +
  geom_path(alpha = .6, color = 'red') +
  geom_point(size = x$Duration*20,  color = '#6291D6', stroke = 1, shape = 21) +
  ggrepel::geom_text_repel(aes(label = Fixation), size = 3, color = 'blue') +
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Scanpath for visual search task (COUNT)') +
  theme_bw() + theme(legend.position = 'none')
## these colors work well for heatmaps (see https://gist.github.com/kalebr/6832380)
jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF",
                                 "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))
z = subset(VS_Fixations, ParticipantID ==	'2019-2_2_f22' & Item == 'fjord.jpg')
#Just heatmap
ggplot(z, aes(x = PositionX, y = 1081-PositionY)) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))),
                 contour=F, n=1000) + 
  scale_alpha(range = c(0.1, 0.6)) +
  scale_fill_gradientn(colours = jet.colors(10), trans="sqrt") + 
  # facet_wrap(~Trial) +
  ## the following lines are for aesthetic purposes only
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Heatmap for visual search task') +
  theme_bw() + theme(legend.position = 'none')
### HEATMAP W/IMAGE
img <- jpeg::readJPEG('Pics/VisualSearch/fjord.jpg')
img <- grid::rasterGrob(img, interpolate=TRUE)
#FINAL PLOT
ggplot(z, aes(x = PositionX, y = 1081-PositionY)) +
  annotation_custom(img, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), # alpha part: the vibrance of the colours are more intense when squarerooted!
                 contour=FALSE, n=1000) + 
  scale_alpha(range = c(0.1, 0.6)) +
  scale_fill_gradientn(colours = jet.colors(10), trans="sqrt") +
  # facet_wrap(~Trial) +
  ## the following lines are for aesthetic purposes only
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Heatmap for visual search task') +
  theme_bw() + theme(legend.position = 'none')
###OTHER CONDITION
x = subset(FixationsVS, ParticipantID ==	'2019-1_1_m11' & Item == 'fjord.jpg')
ggplot(x, aes(x = PositionX, y = 1081-PositionY)) +
  annotation_custom(img, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
  geom_rect(xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf, fill = 'white', alpha = .02) +
  geom_path(alpha = .6, color = 'red') +
  geom_point(size = x$Duration*20,  color = '#6291D6', stroke = 1, shape = 21) +
  ggrepel::geom_text_repel(aes(label = Fixation), size = 3, color = 'blue') +
  xlim(0,1920) + ylim(0,1080) +
  ggtitle('Scanpath for visual search task (STAR)') +
  theme_bw() + theme(legend.position = 'none')
```


###### Social engagement ######
```{r SE Extra data: video info}
# Loading and splitting    
logfiles <- read.csv("logfilesSE.csv")
extraextra <- read.table(text = as.character(logfiles$Video), sep = "_")

# Changing names
logfiles$gender <- extraextra$V1
logfiles$position <- extraextra$V4
logfiles$ostension <- extraextra$V5
 
# Scalin starttime
#Fixations$StartTime_scaled <- scale(Fixations$StartTime)  
#Saccades$StartTime_scaled <- scale(Saccades$StartTime) 

# Separating by 2018
fix18 <- filter(Fixations, Year == "2018")
sac18 <- filter(Saccades, Year =="2018")

# Merging logfiles with 2018 data
allfix18 <- merge(fix18,logfiles)
allsac18 <- merge(sac18,logfiles)

# Filtering out start time length above 5 sec
allfix18 <- filter(allfix18, allfix18$StartTime <= 5000 & allfix18$ParticipantID != "2018-4_1_F")
allsac18 <- filter(allsac18, allsac18$StartTime <= 5000 & allfix18$ParticipantID != "2018-4_1_F")

#Scaling
allfix18$StartTime_scaled <- scale(allfix18$StartTime)
allsac18$StartTime_scaled <- scale(allsac18$StartTime)
 
# ^ Final datasets 
```

```{r Filtering new data }  
fixations_vs <- filter(Fixations, Fixations$Task != "SocialEngagement" & Fixations$StartTime <= 20000 &  Fixations$ParticipantID != "2018-1_1_f1")

fixations_vs <- fixations_vs %>%
  group_by(Trial, ParticipantID) %>%
  filter(Fixation != max(Fixation))

saccades_vs <- filter(Saccades, Saccades$Task != "SocialEngagement" & Saccades$Blink == "FALSE" & Saccades$StartTime <= 20000 & Saccades$ParticipantID != "2018-1_1_f1")
```

Hypotheses
- More emotionally engaged when involved in interaction (~direction & ostensiveness) ---> pupil size
- Direction affects participant attention  ---> direction, amount of saccades
- More focus on person vs. cup when interaction is lead by eye contact --> duration of fixation
- Sexual preferences --> gender
- Familiarity effect  --> participant gender


```{r Pupil size models}  
# Pupil size models 
pup_1 <- glmer(PupilSize ~ ostension * position + (1 | ParticipantID), family = gaussian(link = log), allfix18, REML = F)

pup_2 <- glmer(PupilSize ~ ostension * position + StartTime_scaled + (1 | ParticipantID), family = gaussian(link = log), allfix18, REML = F)

pup_3 <- glmer(PupilSize ~ ostension * position + ParticipantGender * gender + (1 | ParticipantID), family = gaussian(link = log), allfix18, REML = F)

pup_4 <- glmer(PupilSize ~ ostension + position + ParticipantGender * gender + (1 | ParticipantID), family = gaussian(link = log), allfix18, REML = F)

pup_5 <- glmer(PupilSize ~ ParticipantGender * gender + (1 | ParticipantID), family = gaussian(link = log), allfix18, REML = F)

pup_6 <- glmer(PupilSize ~ position + ParticipantGender * gender + (1 | ParticipantID), family = gaussian(link = log), allfix18, REML = F)

pup_7 <- glmer(PupilSize ~ ostension + position + (1 | ParticipantID), family = gaussian(link = log), allfix18, REML = F)

pup_8 <- glmer(PupilSize ~ ParticipantGender * gender + position + StartTime_scaled + (1 | ParticipantID), family = gaussian(link = log), allfix18, REML = F)


allfix18$position_r = relevel(allfix18$position, ref="div")
allfix18$ParticipantGender_r = relevel(allfix18$ParticipantGender, ref="Male")
#FINAL MODEL
pup_9 <- glmer(PupilSize ~ ParticipantGender_r * gender * position_r * ostension + StartTime_scaled + (1 | ParticipantID), family = gaussian(link = log), allfix18, REML = F)


# Summaries
summary(pup_1) #significantly worse than 2            significant position
summary(pup_2) #significantly better than 1           significant time, insignificant interaction    --> main model
summary(pup_3) #same as 2, same as 8                  significant gender interaction
summary(pup_4) #same as 2, worse than 8               significant interaction, significant position
summary(pup_5) #significantly worse than 2            significant interaction
summary(pup_6) #significantly worse than 2            significant interaction, significant position
summary(pup_7) #significantly worse than 2            significant position
summary(pup_8) #significantly better than 2+4         significant interaction, position and time     --> MAIN MODEL
summary(pup_9) #                                      significant 4-way interaction what wohooo´fuck --> MAIN MODEL

#Anovas 
anova(pup_4, pup_8)


#### Familiarity
SE_model_a <- glmer(PupilSize ~ gender * ParticipantGender + (1 | ParticipantID), REML = F, family = gaussian(link = log), allfix18)
summary(SE_model_a)
```

```{r CV} 
MuMIn::r.squaredGLMM(pup_8)
#             R2m       R2c 
# [1,] 1.71602e-07 0.1154295


data_SE <- fold(Fixations2018, k = 2,
                cat_col = c("ParticipantGender", 'Position', 'Gender'), 
             id_col = 'ParticipantID') %>% 
  arrange(.folds)

# To specify models
fixation_model <- ('PupilSize ~ ParticipantGender * Gender + Position + StartTimeS + (1 | ParticipantID)')
  
# To crossvalidate
CV_fix2018 <- cross_validate(data_SE, 
                         fixation_model, 
                         folds_col = '.folds',
                         family = 'gaussian',
                         
                         REML = FALSE)
CV_fix2018
```

```{r Saccades}
attention_1 <- glmer(MeanVelocity ~ position + ostension + (1 | ParticipantID), family = gaussian(link = log), allsac18, REML = F)

summary(attention_1)   # Shite
```

```{r Plots}
allfix18 %>%  
  group_by(ParticipantGender, gender, position, ostension) %>% 
  summarise(PupilMean = mean(PupilSize)) -> PS3

legend_title <- "yello"

PS3 %>% 
  ggplot() +
  aes(x = ParticipantGender, y = PupilMean, color = gender) +
  geom_line(aes(group = gender)) +
  geom_point() + 
  facet_grid(ostension ~ position) +
  labs(x = "Gender of participant", y = "Mean Pupil Size") +
  guides(color=guide_legend(title="Gender of actor"))
         
```


### General info ###
 
```{r Participant info}  
VS_Fixations %>% 
  group_by(ParticipantID, ParticipantGender) %>%
  #unique(ParticipantID) %>%
  #filter(is.na(ParticipantGender)) %>%
  summarise(n())
 
VS_Fixations %>%
  group_by(ParticipantID, Year) %>%
  #unique(ParticipantID) %>%
  #filter(is.na(ParticipantGender)) %>%
  summarise(n())

# 8 female, 4 male, 6 from each year

allfix18 %>%
  group_by(ParticipantID, ParticipantGender) %>% 
  #unique(ParticipantID) %>%
  #filter(is.na(ParticipantGender)) %>%
  summarise(n())

SE_Fixations %>%
  group_by(ParticipantID, Year) %>%
  #unique(ParticipantID) %>%
  #filter(is.na(ParticipantGender)) %>%
  summarise(n())

# 4 female, 2 male = 6 from 2018 (6 from each year)
```















